Radiance - A Web Application Environment

### 2017-03-14 els2017-radiance/paper.tex
Some more fixes.

However, as it currently is, this will obviously not work. The \code{with-caching} macro is not implemented with any useful functionality. As the writer of the paste application, we don't need to know the specifics of how the caching is implemented, though. All we need to do is tell Radiance that we need this interface. This can be done by adding the interface as a dependency to our application's ASDF system definition.

@@

Radiance also does not allow you to change the implementation of an interface on the fly. This has much the same problems as the previous issue. Implementation switching is even more problematic though, since the system needs to ensure that all dependant applications, including optionally dependant ones, are reloaded to make macro redefinitions take effect. Furthermore, since some interfaces expose classes and instances thereof, the system would either have to be able to switch the instances between class definitions, or somehow invalidate the old instances if they are retained in another part of the application. \\

>>>>

However, as it currently is, this will obviously not work. The \code{with-caching} macro is not implemented with any useful functionality. As the writer of the paste application, we don't need to know the specifics of how the caching is implemented, though. All we need to do is tell Radiance that we need this interface. This can be done by adding the interface as a dependency to our application's ASDF\cite{asdf} system definition.

@@

Radiance also does not allow you to change the implementation of an interface on the fly. This has much the same problems as the previous issue. Implementation switching is even more problematic though, since the system needs to ensure that all dependant applications, including optionally dependant ones, are reloaded to make macro redefinitions take effect. Furthermore, since some interfaces expose classes and instances thereof, the system would either have to be able to migrate objects between interface implementations, or somehow invalidate the old instances if they are retained in another part of the application. \\
